DATA 624 Homework 8

### 2020-04-10 DATA624/HW8.Rmd
More work on HW8

pls_predictions <- predict(pls_model, test_df)

@@

#### Neural Network Model

```{r}
nnet_grid <- expand.grid(.decay = c(0, 0.01, .1), .size = c(1:10), .bag = FALSE)
nnet_maxnwts <- 5 * ncol(train_df) + 5 + 1
nnet_model <- train(y ~ ., data = train_df, method = "avNNet",
                    preProcess = c("center"),
                    tuneGrid = nnet_grid,
                    trControl = trainControl(method = "cv"),
                    linout = TRUE,
                    trace = FALSE,
                    MaxNWts = nnet_maxnwts,
                    maxit = 500)
nnet_model

nnet_predictions <- predict(nnet_model, test_df)

results <- data.frame(t(postResample(pred = nnet_predictions, obs = test_df$y))) %>%
  mutate("Model"= "Neural Network") %>% rbind(results)
```

>>>>

pls_model
```

```{r}
pls_predictions <- predict(pls_model, test_df)

@@
